Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 appendix.tex
tex

	\item Why not aa~p~ in ICS?
		less adversarial, further.
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
		works but not good enough.
	\item Another example for the GA pseudo-hardness function family?
		sqaure and sqrt.
	\item Why not ResNet-50?
		ttx and video memory.
	\item fix the anchor like ACT?
		not quite helpful. not necessary.
	\item Why compare in theoretical time cost instead of walltime cost?
		Walltime cost does not precisely indicate the true efficiency
		of a defense method, and may even result in unfair comparison.
		isolate the discrepancy from implementation and engineering tricks,
		as well as software / hardware differences.
	\item full data sheet for tab 2?
		\cref{tab:srcdest}
\end{enumerate}

>>>>

	\item Why not aa~p~ in ICS?
		less adversarial, further.
	\item Have you tried FAT?
	\item What if we mix HM(RM) and HM(SM)?
		works but not good enough.
	\item Another example for the GA pseudo-hardness function family?
		sqaure and sqrt.
	\item Why not ResNet-50?
		ttx and video memory.
	\item fix the anchor like ACT?
		not quite helpful. not necessary.
	\item Why compare in theoretical time cost instead of walltime cost?
		Walltime cost does not precisely indicate the true efficiency
		of a defense method, and may even result in unfair comparison.
		isolate the discrepancy from implementation and engineering tricks,
		as well as software / hardware differences.
	\item full data sheet for tab 2?
		\cref{tab:srcdest}

	\item Details of existing defense methods?

%
Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.
%
However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.

### 2021-10-25 robdml.tex
tex

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{soul}

@@

Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
$\va, \vp, \vn$, respectively.
%
Then the triplet loss~\cite{facenet} is defined as:
%
$
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
%
$
%
where $\gamma$ is a predefined margin parameter.
%
To attack the DML model, an imperceptible adversarial perturbation $\vr$ is
added to the input image $\mX$, which is subject to $\|\vr\|_p \leq
\varepsilon$ and $\mX+\vr\in \mathcal{X}$, so that its embedding vector
$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to 
other positions to fulfill the attacker's goal~[][][][][].

%
Embedding-Shifted Triplet (EST)~\cite{advrank} adopts adversarial counterpars
of $\va,\vp,\vn$ with maximum embedding move distance off their original
locations, \ie,
$L_\text{EST}=L_\text{T}(\tilde{\va},\tilde{\vp},\tilde{\vn};\gamma)$ where
$\tilde{\va}=\phi(X+r^*)$, $r^*=\arg\max_{r}d_\phi(X+r, X)$.
%
Anti-Collapse Triplet (ACT)~\cite{robrank} collapses the embedding vectors of
positive and negative sample, and enforces the model to separate them apart,
\ie, $L_\text{ACT}=L_\text{T}(\va, \overrightarrow{\vp},
\overleftarrow{\vn};\gamma)$, where $[\overrightarrow{\vp},\overleftarrow{\vn}]
=[\phi(X_p+r_p^*), \phi(X_n+r_n^*)]$, and $[r_p^*,r_n^*]=\arg\min_{r_p,r_n}
d_\phi(X_p+r_p, X_n+r_n)$.
%
However, compared to the standard min-max adversarial training
paradigm~\cite{madry}, these methods merely indirectly increase the loss value,
and thus, suffer from inefficient learning because the adversary is not strong
enough.
%
\oo{Furthermore, min-max form -- free adversarial training}.

>>>>

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{comment}

@@

Given a sample triplet of anchor, positive, negative images, \ie, $\mA, \mP,
\mN \in \mathcal{X}$, we first calculate their embeddings with $\phi(\cdot)$ as
$\va, \vp, \vn$, respectively.
%
Then the triplet loss~\cite{facenet} is defined as:
%
$
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
%
$
%
where $\gamma$ is a predefined margin parameter.
%
To attack the DML model, an imperceptible adversarial perturbation $\vr$ is
added to the input image $\mX$, which is subject to $\|\vr\|_p \leq
\varepsilon$ and $\mX+\vr\in \mathcal{X}$, so that its embedding vector
$\tilde{\vx}=\phi(\mX+\vr)$ will be moved off its original location to other
positions to fulfill the attacker's goal~[][][][][].
%
To defend against the attacks, the DML model can be adversarially trained to
reduce the effect of attacks~\cite{advrank,robrank}.
%
The most important metrics for a good defense is training cost, adversarial
robustness, and performance on benign examples.
